### 2014-08-04 Studies/2011_San_Francisco/Report/SF_Fire.tex
San Francisco: Initial commit of report

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1838}
\end{flushright}

\headerB{
Simulation of an Attic Fire \\
in a Wood Frame Residential \\
Structure - Chicago, IL \\
}

@@

\headerC{
{
\flushright{
Craig G. Weinschenk \\
Daniel Madrzykowski \\
Kristopher J. Overholt \\

@@

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}
\endgroup
}

@@

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1838}
\end{flushright}

\headerB{
Simulation of an Attic Fire \\
in a Wood Frame Residential \\
Structure - Chicago, IL \\
}

\headerC{
\flushright{
Craig G. Weinschenk \\
Daniel Madrzykowski \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1838 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
% http://dx.doi.org/10.6028/NIST.TN.1838 \\
CODEN: NTNOEF }

@@

\begin{tabbing}
\hspace{1.5in} \= \\
ft \> foot \\
m \> meter \\
min \> minute \\
Pa \> Pascal \\
psi \> pound per square inch \\
s \> second \\
W \> Watt \\
$k$ \> thermal conductivity \\
$\rho$ \> density \\
$c_{p}$ \> specific heat \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
\addcontentsline{toc}{chapter}{Abstract}
The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain. The inputs for the FDS simulations are documented in this report.  The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure. This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas.  The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.  After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward. The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor. The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at face height.  Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure. The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area. After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.

@@

On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain. NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department. Computer simulations of the fire incident were conducted using Fire Dynamics Simulator and Smokeview to provide insight into the fire development and thermal conditions that might have existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.0.0) simulations.

@@

\begin{figure}[!ht]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
\includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
\end{tabular*}
\caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure. Stairs and key rooms are identified using measurements collected by NIST.}
\label{fig:simp_geom}
\end{figure}

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
   \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
\end{tabular*}
\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
\label{fig:alpha_ex}
\end{figure}
%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
%\begin{figure}[!ht]
%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
%\end{tabular*}
%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
%\label{fig:smv_interior}
%\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
\caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch. Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
\label{fig:door_frame}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
\end{tabular*}
\caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
\label{fig:geom_grid}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
\label{fig:mult_mesh}
\end{figure}

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    &  $k$: 0.12 \; \si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
                                   &  $c_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  &  $k$: 0.28 \; \si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
                                   &  $c_{p}$: 1.0 \; \si{kJ/(kg.K)}                               & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
\caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations. The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
\label{fig:hrr}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
\caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
\label{fig:smv_ext_fire}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
\input{../Scripts/colorbar_metric_pres}
\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure. Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
\label{fig:pres_159s}
\end{figure}

\newpage
\begin{landscape}
\centering
\begin{figure}[!ht]
\includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
\input{../Scripts/colorbar_std_velo}
\input{../Scripts/colorbar_metric_velo}
\caption{FDS simulated velocity vectors, 15~s after interior door failure.}
\label{fig:velo_175s}
\end{figure}
\end{landscape}
\newpage

@@

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
\label{fig:temp_129s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
\label{fig:temp_159s}
\end{figure}

Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}). As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.
\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s after interior door failure.}
\label{fig:temp_161s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 15~s after the interior door failure.}
\label{fig:temp_175s}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
\caption{Post-fire image of interior door.}
\label{fig:chicago_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
   \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
\end{tabular*}
\caption{Post-experiment images of door failures.}
\label{fig:SC_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
\caption{Flow path on the second floor after interior door failure.}
\label{fig:flowpath_1}
\end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. While firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F). This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}). The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases. Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}). Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}). These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch. The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure. Figure~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F). At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas. These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_159}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 5~s after interior door failure.]
{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_165}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 60~s after interior door failure.]
{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_220}
\end{figure}

@@

\chapter{Acknowledgments}
The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck. The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}. Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Simulation of a Basement Fire \\
in a Wood Frame Residential \\
Structure - San Francisco, CA \\
}

@@

\headerC{
{
\flushright{
Kristopher J. Overholt \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\

@@

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Simulation of a Basement Fire \\
in a Wood Frame Residential \\
Structure - San Francisco, CA \\
}

\headerC{
\flushright{
Kristopher J. Overholt \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

\begin{tabbing}
\hspace{1.5in} \= \\
MW \> Megawatt \\
s \> second \\
min \> minute \\
m \> meter \\
ft \> foot \\
Pa \> Pascal \\
psi \> pound per square inch \\
k \> thermal  conductivity \\
$\rho$ \> density \\
c$_{p}$ \> specific heat \\
\end{tabbing}

@@

\chapter*{\centering Abstract}
\addcontentsline{toc}{chapter}{Abstract}
% The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2 story, single family structure in XXXX, that resulted in the death of XXXX. The inputs for the FDS simulations are documented in this report. The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure. This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas. The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door. After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward. The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor. The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at face height. Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure. The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area. After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.

@@

% On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain. NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department. Computer simulations of the fire incident were conducted using Fire Dynamics Simulator and Smokeview to provide insight into the fire development and thermal conditions that might have existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department experienced during the course of their interior operations.
\end{enumerate}
This document describes the input and the results of the FDS (version 6.1.1) simulations.

@@

% \begin{figure}[!ht]
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
% \includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
% \includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
% \end{tabular*}
% \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure. Stairs and key rooms are identified using measurements collected by NIST.}
% \label{fig:simp_geom}
% \end{figure}

% \begin{figure}[!ht]
% \centering
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
%    \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
% \end{tabular*}
% \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
% \label{fig:alpha_ex}
% \end{figure}

%%%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
%%%\begin{figure}[!ht]
%%%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%%%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
%%%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
%%%\end{tabular*}
%%%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
%%%\label{fig:smv_interior}
%%%\end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
% \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch. Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
% \label{fig:door_frame}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%    \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
%    \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
% \end{tabular*}
% \caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
% \label{fig:geom_grid}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
% \caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
% \label{fig:mult_mesh}
% \end{figure}

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    &  k: 0.12 \; \si{W/(m.K)})                                     & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
                                   &  c$_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  &  k: 0.28 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
                                   &  c$_{p}$: 1.0 \; \si{kJ/(kg.K)}                              & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
% \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations. The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
% \label{fig:hrr}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
% \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
% \label{fig:smv_ext_fire}
% \end{figure}

@@

% \begin{figure}[!ht]
% \includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
% \input{../Scripts/colorbar_metric_pres}
% \caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure. Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
% \label{fig:pres_159s}
% \end{figure}

% \newpage
% \begin{landscape}
% \centering
% \begin{figure}[!ht]
% \includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
% \input{../Scripts/colorbar_std_velo}
% \input{../Scripts/colorbar_metric_velo}
% \caption{FDS simulated velocity vectors, 15~s after interior door failure.}
% \label{fig:velo_175s}
% \end{figure}
% \end{landscape}
% \newpage

@@

% \begin{figure}[!ht]
% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
% \label{fig:temp_129s}
% \end{figure}

% \begin{figure}[!ht]
% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
% \label{fig:temp_159s}
% \end{figure}

Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}). As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.

% \begin{figure}[!ht]
% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption{FDS simulated temperature contours, 1~s after interior door failure.}
% \label{fig:temp_161s}
% \end{figure}

% \begin{figure}[!ht]
% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption{FDS simulated temperature contours, 15~s after the interior door failure.}
% \label{fig:temp_175s}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
% \caption{Post-fire image of interior door.}
% \label{fig:chicago_doorfold}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
%    \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
% \end{tabular*}
% \caption{Post-experiment images of door failures.}
% \label{fig:SC_doorfold}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
% \caption{Flow path on the second floor after interior door failure.}
% \label{fig:flowpath_1}
% \end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{designation2003c}. While firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F). This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}). The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases. Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}). Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}). These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch. The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure. Figure~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F). At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas. These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
% {Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
% \label{fig:temp_top_159}
% \end{figure}

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption[Temperature contours on the second floor, 5~s after interior door failure.]
% {Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
% \label{fig:temp_top_165}
% \end{figure}

% \begin{figure}[!ht]
% \centering
% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
% \input{../Scripts/colorbar_std} 
% \input{../Scripts/colorbar_metric}
% \caption[Temperature contours on the second floor, 60~s after interior door failure.]
% {Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
% \label{fig:temp_top_220}
% \end{figure}

@@

\chapter{Acknowledgments}
The authors would like to thank XXXX. The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
